Modeling memory and taxis to analyze migrations

### 2021-06-21 text/ms.Rmd
exploring ...

@@

@@

**Describing conditions for adaptability.**

>>>>

A random forest analysis indicated that the most important variables for attaining optimal migratory behavior were $\alpha$ and $\lambda$, and the least important, consistently, was $\sigma_t$ (table **X**).

@@

The model had, in general, a difficult time learning migration from a non-migratory initial condition.  Curiously, the conditions that were more conducive to learning migration were pulses of *longer* duration (high $\sigma_t$)
 but narrow spatial extent (low $\sigma_x$).  This was in contrast to the conditions that were most amenable for stable migratory behavior (high $\sigma_x$, intermediate $\sigma_t$).   Furthermore

@@

**Describing conditions for adaptability / stability.**
